---
title: "User Manual"
author: "Sören Künzel and Ling Xie"
date: "12/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Getting Started

### Example 1: The GOTV data set.
The *gotv* data set is part of the *causalToolbox* library and it was taken from
Gerber AS, Green DP, Larimer CW (2008). It contains 229,461 observations. For
each of them we observe seven covariates: **sex**, **age**, and whether or not
they have voted in the general election 2000 and 2002 or the primary election
2000 and 2002. The goal of this study was to increase voter turnout (**voted**)
in the 2006 primary election. The authors used a mailer that is indicated in the
**treatment** column. For treated units the treatment variable is equal to 1 and
for units in the control group, the treatment indicator is equal to 0.
```{r, read in data, cache=TRUE}
library(causalToolbox)
head(gotv)
```

To estimate the CATE, we first have to train a CATE estimator. The package
implements eight different estimators: **MO_RF, S_RF, T_RF, and X_RF** are based
on the [forestry package](https://github.com/soerenkuenzel/forestry) and
**MO_BART, S_BART, T_BART, and X_BART** are based on the [dbarts
package](https://cran.r-project.org/web/packages/BART/index.html).

```{r, tRF CI, cache=TRUE}
set.seed(30019455)
train_ids <- sample.int(nrow(gotv), 1000)
test_ids <- sample((1:nrow(gotv))[-train_ids], 5)

feat <- gotv[train_ids , -(8:9)]
tr <- gotv$treatment[train_ids]
yobs <- gotv$voted[train_ids]

t_rf <- T_RF(feat = feat, tr = tr, yobs = yobs)
cate_t_rf <- EstimateCate(t_rf, gotv[test_ids, ])
cateCI <- CateCI(t_rf, gotv[test_ids, ], B = 200, verbose = FALSE)
cateCI
```
It is straight foward to use other Cate estimators.
```{r, several learners, cache=TRUE}
set.seed(50245181)

s_rf <- S_RF(feat = feat, tr = tr, yobs = yobs)
cate_s_rf <- EstimateCate(s_rf, gotv[test_ids, ])
x_bart <- X_BART(feat = feat, tr = tr, yobs = yobs)
cate_x_bart <- EstimateCate(x_bart, gotv[test_ids, ])
t_bart <- T_BART(feat = feat, tr = tr, yobs = yobs)
cate_t_bart <- EstimateCate(t_bart, gotv[test_ids, ])

cbind(cate_t_rf, cate_s_rf, cate_x_bart, cate_t_bart) 
```

### Example 2: Generating Examples
The *causalToolbox* package also implements a method to simulate many data sets:
```{r, simulated Example 2, cache = TRUE}
simulated_experiment <- simulate_causal_experiment(
  ntrain = 1000,
  ntest = 1000,
  dim = 10,
  setup = "complexTau",
  testseed = 293901,
  trainseed = 307017
)
```

This can be used to compare the different estimators in terms of MSE.

```{r, Example 2 run experiments, cache = TRUE}
feat <- simulated_experiment$feat_tr
tr <- simulated_experiment$W_tr
yobs <- simulated_experiment$Yobs_tr
feature_test <- simulated_experiment$feat_te

# create the hte object using honest Random Forests (RF)
xl_rf <- X_RF(feat = feat, tr = tr, yobs = yobs, verbose = FALSE)
tl_rf <- T_RF(feat = feat, tr = tr, yobs = yobs)
sl_rf <- S_RF(feat = feat, tr = tr, yobs = yobs)

cate_esti_xrf <- EstimateCate(xl_rf, feature_test)
cate_esti_trf <- EstimateCate(tl_rf, feature_test)
cate_esti_srf <- EstimateCate(sl_rf, feature_test)

# evaluate the performance
cate_true <- simulated_experiment$tau_te
c("mse_xrf" = mean((cate_esti_xrf - cate_true) ^ 2), 
  "mse_trf" = mean((cate_esti_trf - cate_true) ^ 2), 
  "mse_srf" = mean((cate_esti_srf - cate_true) ^ 2))
```

One can also access the coverage of confidence intervals. 

```{r, Example 2 get CIs, cache = TRUE}
ci_srf <- CateCI(tl_rf, feature_test, B = 200, verbose = FALSE)
mean(ci_srf$X5. < cate_true & ci_srf$X95. > cate_true)
```
